---
title: "Re_Analysis of IMI Trial"
author: "Yunhe Liu"
date: "2024-10-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###  Implementation
This section provides R implementation of the model described above.
The required R packages are:
```{r}
#rm(list=ls(all=TRUE))
library(RBesT)
library(randomizr)
library(reshape2)
library(GGally)
library(foreach)
require(LearnBayes)
library(mvtnorm)
```


##Source fundtions used in case study
```{r}
setwd("/Users/iad/Desktop/Study/Yale/Research/Wei Wei Project TDB /code")
source("reg_bma_2.R")
source("myfun.R")
source("mem functions.R")
source("exnex.R")
```


##Change some functions better used in case study estimates
```{r}
## b0_prior: (mean, sd, weight of this component)
## b1_prior: (mean, sd)
## pess_prior: pess prior for each indication
## enth_prior: enth prior for each indication
## mod_prior: prior weight for each model of consideration

## set up all the models: 
## B: number of indications
init.mod <- function(B, prior_indicator){
  zero_one <- list()
  #1 is promising, 0 is not promising
  for(b in 1:B) zero_one[[b]] <- prior_indicator
  mods <- expand.grid(zero_one)
  names(mods) <- LETTERS[1:B]
  mods
}

gen.prior <- function(mods, r){
  B <- ncol(mods)
  tab0 <- rbind(table(rowSums(mods==1)), (1+0:B)^r/sum((1+0:B)^r))
  prior <- tab0[2, 1+rowSums(mods==1)]/tab0[1, 1+rowSums(mods==1)]
  
  sim_mat <- diag(1, B, B)
  for(i in 1:B){
    for(j in 1:B){
      if(i==j){sim_mat[i, j] <- 1}
      if(i!=j){
        sim_mat[i, j] <- sim_mat[j, i] <- sum((mods[, i]*mods[, j]==1)*prior)
      }
    }
  }
  rownames(sim_mat) <- colnames(sim_mat) <- paste("IND", 1:B, sep="")
  
  list("tab" = tab0, "prior"=prior, "sim" = sim_mat)
}

post.den <- function(betas, b0_prior, b1_prior, x, y, log = T){
  b0 <- betas[1]
  b1 <- betas[2]
  lik <- prod(ifelse( y==1, exp(b0+b1*x)/(1+exp(b0+b1*x)), 
                      1/(1+exp(b0+b1*x)) ))
  ##prior density of intercept b0
  den0 <- b0_prior[3]*dnorm(b0, b0_prior[1], b0_prior[2])+
    (1-b0_prior[3])*dnorm(b0, 0, 100)
  ##prior density of slope b1
  den1 <- dnorm(b1, b1_prior[1], b1_prior[2])
  post <- lik*den0*den1
  if(log){
    log(post)
  }else{
    post
  }
}

## y: response to treatment
## x: treatment assignment

mlik <- function(y, x, b0_prior, b1_prior, approxi = TRUE){
  if(approxi){
    inits <- c(as.numeric(glm(y ~ 1, family = binomial)$coef), 0)
    logmp <- laplace(post.den, inits, b0_prior = b0_prior, b1_prior = b1_prior,
                     y = y, x = x)$int
    exp(logmp)
  }else{
    adaptIntegrate(post.den, b0_prior = b0_prior, b1_prior = b1_prior,
                   y = y, x = x, log = FALSE, 
                   lowerLimit=c(-100,-100),
                   upperLimit=c(100, 100))$integral
  }
}

update.mod.wt <- function(dat, b0_prior_mat, pess_prior, enth_prior, mod_prior, 
                          approxi = TRUE){
  B <- ncol(pess_prior)
  ## list all the models to average
  ## rows are models, columns are indications
  mods <- init.mod(B, prior_indicator = c(0, 1))
  ## marginal likelihood of each indication under 
  ## pessimisitc and enthusiastic priors
  mar_lik <- matrix(NA, nrow = 2, ncol = B)
  rownames(mar_lik) <- c("pess", "enth")
  
  for(b in 1:B){
    y <- dat[[b]]$outcome
    x <- dat[[b]]$trt
    
    if(approxi==FALSE){
      mar_lik[1, b] <- mlik(y = y, x = x, b0_prior = b0_prior_mat[b, ], 
                            b1_prior = pess_prior[, b], approxi = FALSE)
      
      mar_lik[2, b] <- mlik(y = y, x = x, b0_prior = b0_prior_mat[b, ], 
                            b1_prior = enth_prior[, b], approxi = FALSE)
    }
    if(approxi){
      mar_lik[1, b] <- mlik(y = y, x = x, b0_prior = b0_prior_mat[b, ], 
                            b1_prior = pess_prior[, b])
      
      mar_lik[2, b] <- mlik(y = y, x = x, b0_prior = b0_prior_mat[b, ], 
                            b1_prior = enth_prior[, b])
    }
  }
  
  p <- NULL
  for(k in 1:nrow(mods)){
    idx0 <- (mods[k, ]==0)
    idx1 <- (mods[k, ]==1)
    p[k] <- prod(ifelse(mods[k, ]==0, mar_lik[1, ], mar_lik[2, ]))*mod_prior[k]
  }
  ## calculate posterior prob of each grouping structure
  mods$p <- p/sum(p)
  
  list("mlik" = mar_lik, "mods" = mods)
}

fit.bma <- function(dat, b0_prior_mat, pess_prior, enth_prior, mod_prior, 
                    post_enth_wt, approxi = TRUE, beta_ni = NULL){
  result <- NULL
  for(b in 1:ncol(pess_prior)){
    y <- dat[[b]]$outcome
    x <- dat[[b]]$trt
    
    inits <- c(as.numeric(glm(y ~ 1, family = binomial)$coef), 0)
    
    post_fit0 <- laplace(post.den, inits, b0_prior = b0_prior_mat[b, ], 
                         b1_prior = pess_prior[, b], y = y, x = x)
    post_sim0 <- rmvnorm(5000, mean = post_fit0$mode, sigma = post_fit0$var)
    
    post_fit1 <- laplace(post.den, inits, b0_prior = b0_prior_mat[b, ], 
                         b1_prior = enth_prior[, b], y = y, x = x)
    post_sim1 <- rmvnorm(5000, mean = post_fit1$mode, sigma = post_fit1$var)
    ## the mixture of two models
    mod_ind <- rbinom(n = 5000, size = 1, prob = post_enth_wt[b])
    post_sim <- rbind(post_sim1[mod_ind==1, ], post_sim0[mod_ind==0, ])
    est <- quantile(post_sim[, 2], c(0.025, 0.5, 0.975))
    
    #Calculate estimated mortality rate
    logit_trt <- as.vector(post_sim[, 1]+post_sim[, 2])
    Diff      <- exp(logit_trt)/(1+exp(logit_trt)) - exp(post_sim[, 1])/(1+exp(post_sim[, 1]))
    est_diff  <- mean(Diff)
    qua_diff  <- quantile(Diff, c(0.025, 0.5, 0.975))
    
    if(is.null(beta_ni)){
      pp <- mean(post_sim[, 2]<0)
    }else{
      pp <- mean(post_sim[, 2]<beta_ni)
    }
    
    result <- rbind(result, c(qua_diff, pp, est_diff))
  }
  result <- data.frame(result)
  names(result) <- c("q2.5", "q50", "q97.5", "pp", "bias")
  result
}
```


### Example
Invasive mould infections (IMIs), such as invasive aspergillosis or mucormycosis, are a major cause of death in patients with hematological cancer and in patients receiving long-term immunosuppressive therapy. People, especially those with weakened immune systems, can develop invasive mold infections days to weeks after exposure to fungi that live in the environment. These infections are rare, difficult to diagnose and often life-threatening. Antifungal clinical trials have always been difficult to recruit patients due to the relatively small number patients with the specific invasive fungal infection (~ 1.5/site/year). The trials are logistically complex, take a long time to conduct and are require much resources (people and money). FDA has issued the limited population pathway for antibacterial and antifungal drugs (LPAD pathway) guidance document, for drugs intended to treat a serious or life-threatening infection in a limited population of patients with unmet needs and permits the risk-benefit assessment to flexibly consider severity, rarity, and prevalence of infection the drug is intended to treat, however LPAD pathway does not alter FDA approval standards which requires randomized comparison. The common practice is to perform analysis combining all fungal pathogens. 

We analyze a hypothetical trial data where participants were be randomized in a 2:1 ratio to an experimental treatment or standard of care (SOC) based on the confirmed or suspected fungal species. The primary endpoint was day 42 survival rate. Improvement in day 42 survival rate indicates efficacy of experimental treatment. 
```{r}
## simulate data for a randomized basket trial
sim.dat <- function(n_soc, n_trt, p_soc, p_trt){
  ## sample size of each indication
  ind_size <- n_soc + n_trt
  ## number of indications
  B <- length(p_soc)
  ## response rate (trt*indication)
  pmat <- rbind(p_soc, p_trt)
  ## sample size (trt*indication)
  rownames(pmat) <- c("soc", "trt")
  colnames(pmat) <- paste("IND-", LETTERS[1:B], sep = "")
  
  rawdat <- list()
  ## aggregated data
  y_soc <- y_trt <- NULL
  for(b in 1:B){
    ## randomize within each indication
    trt <- complete_ra(N = ind_size[b],  m = n_trt[b])
    ## response probability of each patient in indication b
    pvec <- pmat[1+trt, b]
    outcome <- rbinom(n = ind_size[b], size = 1, prob = pvec)
    rawdat[[b]] <- data.frame("trt"=trt, "outcome"=outcome)
    y_trt[b] <- sum(outcome[trt==1])
    y_soc[b] <- sum(outcome[trt==0])
  }
  
  summary_data <- data.frame(n_soc = n_soc, n_trt = n_trt, 
                             y_soc = y_soc, y_trt = y_trt)
  
  list("raw_data" = rawdat, "summary_data" = summary_data)
}


# Determines amount of prior enthusiasm we have for the experimental treatments 
r <- 0
# Noninferiority margin
ni_mar <- 0.05
## ----------------------------------------------------------------
## current trial:
## Participants will be randomized in a 2:1 ratio to an 
## experimental treatment or standard of care (SOC) based on 
## the confirmed or suspected fungal species. Below are the 
## details of comparator and sample size for each pathogen. 
##Fungal Pathogen	SOC	N (Trt/Control)
## Fusarium	L-AmB +/- VORI	20/10
## Scedosporium	VORI +/- other AF	15/7
## Lomentospora	VORI + TERB  (+/- other AF)	15/7
## Aspergillus	L-AmB +/-CAN	30/15
## Mucorales	L-AmB +/- other AF or ISA monoRx	20/10
## ----------------------------------------------------------------
# randomization ratio of trt vs. ctr
R <- 2
ind_name <- c("Fusarium", "Scedosporium", "Lomentospora", "Aspergillus", 
              "Mucorales")
# below are the assumed true death rates we simulate from:
# day42 death rates for SOC
p0 <- c(0.60, 0.88, 0.70, 0.51, 0.67)
# day42 death rates for the treatment:
p1 <- p0 - 0.30
## ----------------------------------------------------------------
# B: the number of indications 
B <- length(p0)
# ind_size: the total sample size of each indication
ind_size <- c(30, 22, 22, 45, 30)
n_soc <- c(10, 7, 7, 15, 10)
n_trt <- c(20, 15, 15, 30, 20)
## ----------------------------------------------------------------
## historical control:
## ----------------------------------------------------------------
## sample size of relevant historical controls:
nh <- c(112, 89, 20, 37, 21)
## number of day42 deaths in historical controls
rh <- c(66, 78, 14, 19, 14)
## ----------------------------------------------------------------
## set up the simulation study
## ----------------------------------------------------------------
# pmat0/pmat1: matrix of response rates for the SOC/trt 
## rows: scenarios
## columns: indications
pmat0 <- matrix(rep(c(0.6, 0.88, 0.7, 0.51, 0.67), 6), nrow = 6, byrow = TRUE)
# pmat1 <- matrix(c(0.65, 0.30, 0.30, 0.30, 0.30, 0.30,
#                   0.93, 0.93, 0.58, 0.58, 0.58, 0.58,
#                   0.75, 0.75, 0.75, 0.40, 0.40, 0.40,
#                   0.56, 0.56, 0.56, 0.56, 0.21, 0.21,
#                   0.72, 0.72, 0.72, 0.72, 0.72, 0.37),
#                   nrow = 6, byrow = FALSE)
pmat1 <- matrix(c(0.65, 0.45, 0.45, 0.45, 0.45, 0.45,
                  0.93, 0.93, 0.73, 0.73, 0.73, 0.73,
                  0.75, 0.75, 0.75, 0.55, 0.55, 0.55,
                  0.56, 0.56, 0.56, 0.56, 0.36, 0.36,
                  0.72, 0.72, 0.72, 0.72, 0.72, 0.52),
                  nrow = 6, byrow = FALSE)
```


Here, we consider five scenarios in our data generation and we take the scenario
3 as illustration. Scenario 1 is the global null scenario, the D42-mortality rate 
is 0.65, 0.93, 0.75, 0.56 and 0.72 for the the treatment and control arms of 
each indication. Under scenarios 2, · · · , 5, the experimental treatment succeeds 
in some indications (reaching the target mortality rate) but fails in other 
indications. 


```{r}
Case.Study <- function(trial_dat){
  ##Test Decision: Posterior Probability Threshold
  gam_ref   <- rep(0.9832, 5)
  gam_bma   <- rep(0.9806, 5)
  gam_bma2D <- rep(0.9618, 5)
  gam_nex   <- rep(0.9754, 5)
  gam_nex2D <- rep(0.9706, 5)


  ## ----------------------------------------------------
  ## Reference method without any borrowing
  ## ----------------------------------------------------
  trial_summary <- sim_out$summary_data
  trial_summary$Disease <- c("Fusarium", "Scedosporium", "Lomentospora", 
                            "Aspergillus", "Mucorales")
  # Test Decision
  ref.pp <- 1 - no.borrow(trial_summary, ni_mar = ni_mar)
  decision.ref  <- ref.pp > gam_ref
  #Calculate mortality rate difference (treatment effect) est
  phat0 <- (sim_out$summary_data$y_soc + 1) / (sim_out$summary_data$n_soc + 2)
  phat1 <- (sim_out$summary_data$y_trt + 1) / (sim_out$summary_data$n_trt + 2)
  est.ref <- (phat1 - phat0)
  #Calculate mortality rate difference 95% credible interval
  samples.phat0 <- matrix(0, nrow = 5000, ncol = length(pmat1[s,]))
  samples.phat1 <- matrix(0, nrow = 5000, ncol = length(pmat1[s,]))
  for (i in 1:length(pmat1[s,])) {
    samples.phat0[, i] <- rbeta(5000,sim_out$summary_data$y_soc[i] + 1,
                          (sim_out$summary_data$n_soc[i] - sim_out$summary_data$y_soc[i]) + 1)
  }
  for (j in 1:length(pmat1[s,])) {
    samples.phat1[, j] <- rbeta(5000, sim_out$summary_data$y_trt[j] + 1,
                          (sim_out$summary_data$n_trt[j] - sim_out$summary_data$y_trt[j]) + 1)
  }
  samples.diff   <- samples.phat1 - samples.phat0
  credible.ref   <- apply(samples.diff, 2, function(column) quantile(column, c(0.025, 0.975)))
  
  
  ## ----------------------------------------------------
  ## naive pooling
  ## ----------------------------------------------------
  pooled <- colSums(sim_out$summary_data)
  phat0 <- pooled[3] / pooled[1]
  phat1 <- pooled[4] / pooled[2]
  se <- sqrt(phat0 * (1 - phat0) / pooled[1] + phat1 * (1 - phat1) / pooled[2])
  zval.pool <- (phat1 - phat0 - ni_mar) / se
  # Test Decision
  decision.pool <- rep(zval.pool < qnorm(0.1), 5)
  names(decision.pool) <- NULL
  pvalue.pool <-  pnorm(unique(zval.pool))
  #Calculate mortality rate difference (treatment effect) est
  est.pool <- as.numeric(phat1 - phat0)
  #Calculate mortality rate difference 95% confidence interval
  alpha <- 0.05
  z_alpha_2  <- qnorm(1 - alpha / 2)
  se <- as.numeric(sqrt(phat0*(1-phat0)/pooled[1] + phat1*(1-phat1)/pooled[2]))
  pool.lower <- rep(as.numeric(phat1 - phat0), 5) - rep(z_alpha_2 * se, 5)
  pool.upper <- rep(as.numeric(phat1 - phat0), 5) + rep(z_alpha_2 * se, 5)
  confidence.pool <- rbind(pool.lower, pool.upper)
  rownames(confidence.pool) <- c("2.5%", "97.5")
  
  
  ## ----------------------------------------------------
  ## Test&Pool
  ## ----------------------------------------------------
  pooled <- colSums(sim_out$summary_data)
  phat0 <- pooled[3] / pooled[1]
  phat1 <- pooled[4] / pooled[2]
  se <- sqrt(phat0 * (1 - phat0) / pooled[1] + phat1 * (1 - phat1) / pooled[2])
  zval.test.pool<- (phat1 - phat0 - ni_mar) / se
  # Test Decision
  decision.test.pool <- rep(zval.test.pool< qnorm(0.1), 5)
  names(decision.test.pool) <- NULL
  pvalue.test.pool <-  pnorm(unique(zval.test.pool))
  #Calculate mortality rate difference (treatment effect) est
  est.test.pool <- as.numeric(phat1 - phat0)
  #Calculate mortality rate difference 95% confidence interval
  alpha <- 0.05
  z_alpha_2  <- qnorm(1 - alpha / 2)
  se <- as.numeric(sqrt(phat0*(1-phat0)/pooled[1] + phat1*(1-phat1)/pooled[2]))
  test.pool.lower <- rep(as.numeric(phat1-phat0), 5) - rep(z_alpha_2*se, 5)
  test.pool.upper <- rep(as.numeric(phat1-phat0), 5) + rep(z_alpha_2*se, 5)
  confidence.test.pool <- rbind(test.pool.lower, test.pool.upper)
  rownames(confidence.test.pool) <- c("2.5%", "97.5")
  ## ----------------------------------------------------
  ## if pooled result is significant, then proceed with individual tests:
  ## ----------------------------------------------------
  pval <- pnorm(unique(zval.test.pool))
  if (pval < 0.1) {
    phat0 <- sim_out$summary_data$y_soc / sim_out$summary_data$n_soc
    phat1 <- sim_out$summary_data$y_trt / sim_out$summary_data$n_trt
    se <- sqrt(phat0*(1-phat0)/sim_out$summary_data$n_soc + phat1*(1-phat1)/sim_out$summary_data$n_trt)
    zval.test.pool<- (phat1 - phat0 - ni_mar) / se
    # Test Decision
    decision.test.pool <- zval.test.pool< qnorm(0.1/5)
    names(decision.test.pool) <- NULL
    pvalue.test.pool <-  pnorm(zval.test.pool)
    #Calculate mortality rate difference (treatment effect) est
    est.test.pool <- as.numeric(phat1 - phat0)
    #Calculate mortality rate difference 95% credible
    alpha <- 0.05
    z_alpha_2  <- qnorm(1 - alpha / 2)
    test.pool.lower <- as.numeric(phat1 - phat0) - z_alpha_2 * se
    test.pool.upper <- as.numeric(phat1 - phat0) + z_alpha_2 * se
    confidence.test.pool <- rbind(test.pool.lower, test.pool.upper)
    rownames(confidence.test.pool) <- c("2.5%", "97.5")
  }
  
  
  ## ----------------------------------------------------------------
  # B: the number of indications
  B <- length(p0)
  ## ----------------------------------------------------------------
  ## historical control:
  ## ----------------------------------------------------------------
  ph <- rh / nh
  ## unit information of the log odds for SOC
  u <- ph * (1 - ph)
  ## sd of the prior for log odds
  sd0 <- sqrt((u * n_soc) ^ (-1))
  m0 <- log(ph / (1 - ph))
  
  ## ----------------------------------------------------------------
  ## enthusiastic and pessimistic priors:
  ## design priors represent the state of knowledge about
  ## SOC or treatment, they should not overlap too much
  ## the selection of design priors can be informed by historical trials or
  ## based on expert opinions. If there are multiple historical trials,
  ## map can be used.
  ## previous trials and external data might not have the biomarkers needed
  ## ----------------------------------------------
  pess_prior <- enth_prior <- matrix(NA, nrow = 2, ncol = length(p1))
  for (b in 1:B) {
    n11 <- ind_size[b] * (R / (R + 1)) * p1[b]
    n10 <- ind_size[b] * (R / (R + 1)) * (1 - p1[b])
    n01 <- ind_size[b] * (1 / (R + 1)) * (p0[b])
    n00 <- ind_size[b] * (1 / (R + 1)) * (1 - p0[b])
    v <- sum(c(n11, n10, n01, n00) ^ (-1))
    #pess_prior[, b] <- c(0, sqrt(v))
    #assume it is worse
    pess_prior[, b] <- c(logit(p0[b] + ni_mar) - logit(p0[b]), sqrt(v))
    enth_prior[, b] <- c(logit(p1[b]) - logit(p0[b]), sqrt(v))
  }
  ## ----------------------------------------------------------------
  ## select the method for BMA
  ## ----------------------------------------------------------------
  bma_mods <- init.mod(B, prior_indicator = c(0, 1))
  bma_prior <- gen.prior(mods = bma_mods, r = r)$prior
  ## ----------------------------------------------------
  ## BMA: learning across indications
  ## ----------------------------------------------------
  b0_prior_mat <- cbind(rep(0, B), rep(5, B), 1)
  
  post_mod_wt <- update.mod.wt(dat = trial_dat, b0_prior_mat = b0_prior_mat, pess_prior = pess_prior,
                               enth_prior = enth_prior, mod_prior = bma_prior)$mods
  
  post_enth_wt <- colSums(post_mod_wt[, 1:B] * post_mod_wt$p)
  
  beta_ni <- log((p0 + ni_mar) / (1 - (p0 + ni_mar))) - log(p0 / (1 - p0))
  
  fit <-fit.bma(dat = trial_dat, b0_prior_mat = b0_prior_mat, pess_prior = pess_prior,
                enth_prior = enth_prior, mod_prior = bma_prior, 
                post_enth_wt = post_enth_wt, beta_ni = beta_ni)
  # Test Decision
  bma.pp <- fit$pp
  decision.bma <- bma.pp > gam_bma
  names(decision.bma) <- NULL
  #Calculate mortality rate difference (treatment effect) est
  est.bma <- fit$bias
  #Calculate mortality rate difference 95% credible interval
  bma.lower <- fit$q2.5
  bma.upper <- fit$q97.5
  credible.bma <- rbind(bma.lower, bma.upper)
  rownames(credible.bma) <- c("2.5%", "97.5")
  
  
  ## ----------------------------------------------------
  ## BMA two dimensional learning
  ## ----------------------------------------------------
  b0_prior_mat <- cbind(m0, sd0, 0.5)
  
  post_mod_wt <- update.mod.wt(dat = trial_dat, b0_prior_mat = b0_prior_mat, pess_prior = pess_prior,
                               enth_prior = enth_prior, mod_prior = bma_prior)$mods
  
  post_enth_wt <- colSums(post_mod_wt[, 1:B] * post_mod_wt$p)
  
  fit <- fit.bma(dat = trial_dat, b0_prior_mat = b0_prior_mat, pess_prior = pess_prior,
                 enth_prior = enth_prior, mod_prior = bma_prior,
                 post_enth_wt = post_enth_wt, beta_ni = beta_ni)
  # Test Decision
  bma.2D.pp <- fit$pp
  decision.bma.2D <- bma.2D.pp > gam_bma2D
  #Calculate mortality rate difference (treatment effect) est
  est.bma.2D <- fit$bias
  #Calculate mortality rate difference 95% credible interval
  bma.2D.lower <- fit$q2.5
  bma.2D.upper <- fit$q97.5
  credible.bma.2D <- rbind(bma.2D.lower, bma.2D.upper)
  rownames(credible.bma.2D) <- c("2.5%", "97.5")
  
  
  ## prior ess for borrowing from historical trial
  prior_n <- n_soc
  # Informative prior for the control arm using exnex
  infor_prior_ab <- cbind(prior_n * rh / nh, prior_n * (nh - rh) / nh)
  ## ----------------------------------------------------
  ## EXNEX
  ## ----------------------------------------------------
  trial_summary$x_soc <- trial_summary$n_soc - trial_summary$y_soc
  
  nex_anal <- Model_EXEX_rand (
    y.t = trial_summary$y_trt,
    n.t = trial_summary$n_trt,
    group       = 1:B,
    group.nm    = trial_summary$Disease,
    Prior.mu.t  = c(log(4), 1),
    Prior.tau.t = c(0, 0.5),
    p.exch.t    = 0.5,
    tau.index   = 1,
    Prior.nex.t = cbind(rep(0, B), rep(2, B)),
    pars = c("p.t", "tau.t", "Z.t"),
    MCMC = c(5000, 10000, 1, 1),
    DIC = TRUE,
    seed = 19978
  )
  
  pt_mcmc <- nex_anal$sim$p.t
  
  pc_mcmc <- NULL
  for (basket in 1:B) {
    pc_mcmc <-
      cbind(pc_mcmc,
            rbeta(5000, 1 + trial_summary$y_soc[basket], 1 + trial_summary$x_soc[basket]))
  }
  # Test Decision
  nex.pp <- colMeans(pt_mcmc < pc_mcmc + ni_mar)
  decision.nex <- nex.pp > gam_nex
  names(decision.nex) <- NULL
  #Calculate mortality rate difference (treatment effect) est
  est.nex <- as.numeric(colMeans(pt_mcmc) - colMeans(pc_mcmc))
  #Calculate mortality rate difference 95% credible interval
  nex.diff     <- pt_mcmc - pc_mcmc
  colnames(nex.diff) <- NULL
  credible.nex <- apply(nex.diff, 2, function(column)quantile(column, c(0.025, 0.975)))
  
  
  ## ----------------------------------------------------
  ## EXNEX-2D
  ## ----------------------------------------------------
  pc_mcmc <- NULL
  for (basket in 1:B) {
    ## beta mixture priors
    bm_prior <-
      mixbeta(rob = c(0.5, 1, 1),
              inf = c(0.5, infor_prior_ab[basket,]))
    bm_post <-
      postmix(priormix = bm_prior,
              n = trial_summary$n_soc[basket],
              r = trial_summary$y_soc[basket])
    
    pc_mcmc <- cbind(pc_mcmc, rmix(bm_post, 5000))
  }
  # Test Decision
  nex.2D.pp <- colMeans(pt_mcmc < pc_mcmc + ni_mar)
  decision.nex.2D <- nex.2D.pp > gam_nex2D
  names(decision.nex.2D) <- NULL
  #Calculate mortality rate difference (treatment effect) est
  est.nex.2D <- as.numeric(colMeans(pt_mcmc) - colMeans(pc_mcmc))
  #Calculate mortality rate difference 95% credible interval
  nex.2D.diff     <- pt_mcmc - pc_mcmc
  colnames(nex.2D.diff) <- NULL
  credible.nex.2D <- apply(nex.2D.diff, 2, function(column) quantile(column, c(0.025, 0.975)))
  
  
  # Test Decision Comparison
  decision.comparison <- cbind(decision.pool, decision.test.pool, decision.ref,
                               decision.bma, decision.nex,
                               decision.bma.2D, decision.nex.2D)
  decision.comparison <- as.data.frame(decision.comparison)
  rownames(decision.comparison) <- c("Fusarium", "Scedosporium", "Lomentospora", 
                                     "Aspergillus", "Mucorales")
  
  # Test Decision Evidence Comparison
  decision.evidence <- cbind(pvalue.pool, pvalue.test.pool, ref.pp,
                             bma.pp, nex.pp,
                             bma.2D.pp, nex.2D.pp)
  decision.evidence <- round(decision.evidence, 4)
  decision.evidence <- as.data.frame(decision.evidence)
  rownames(decision.evidence) <- c("Fusarium", "Scedosporium", "Lomentospora", 
                                     "Aspergillus", "Mucorales")
  
  # Mortality Rate Difference (Treatment Effect) Est Comparison
  est.comparison <- cbind(est.pool, est.test.pool, est.ref,
                          est.bma, est.nex, est.bma.2D, est.nex.2D)
  est.comparison <- as.data.frame(est.comparison)
  rownames(est.comparison) <- c("Fusarium", "Scedosporium", "Lomentospora", 
                                "Aspergillus", "Mucorales")
  
  # Mortality Rate Difference 95% Confidence/Credible Interval Comparison
  # Define a function to combine lower and upper limits into a string with parentheses, aligned with three significant digits
  combine_ci_aligned <- function(lower, upper) {
    lower_formatted <-
      sprintf("%6.2f", lower)  # Remove leading space for the lower bound
    upper_formatted <-
      sprintf("%6.2f", upper)  # Remove leading space for the upper bound
    return(paste0("(", lower_formatted, ", ", upper_formatted, ")"))
  }
  # Construct the data frame with aligned confidence intervals
  ci.comparison <- data.frame(
    Method1 = combine_ci_aligned(confidence.pool[1, ], confidence.pool[2, ]),
    Method2 = combine_ci_aligned(confidence.test.pool[1, ], confidence.test.pool[2, ]),
    Method3 = combine_ci_aligned(credible.ref[1, ], credible.ref[2, ]),
    Method4 = combine_ci_aligned(credible.bma[1, ], credible.bma[2, ]),
    Method5 = combine_ci_aligned(credible.nex[1, ], credible.nex[2, ]),
    Method6 = combine_ci_aligned(credible.bma.2D[1, ], credible.bma.2D[2, ]),
    Method7 = combine_ci_aligned(credible.nex.2D[1, ], credible.nex.2D[2, ])
  )
  # Set column names for the output data frame
  colnames(ci.comparison) <- c("Pool", "Test&Pool", "Reference",
                               "BMA", "EXNEX", "BMA-2D", "EXNEX-2D")
  rownames(ci.comparison) <- c("Fusarium", "Scedosporium", "Lomentospora", 
                               "Aspergillus", "Mucorales")
  
  # Define a function to combine point estimate and confidence intervals into "point_estimate (lower, upper)" format
  # Both point estimate and confidence interval are formatted to three significant digits
  combine_point_ci <- function(point, ci) {
    point_formatted <-
      sprintf("%6.2f", point)  # Format point estimate to three significant digits
    return(paste0(point_formatted, " ", ci))  # Combine point estimate and confidence interval with a space
  }
  
  # Create a new data frame by combining point estimates and confidence intervals
  combined.inf <- data.frame(
    Method1 = mapply(combine_point_ci, est.comparison[, 1], ci.comparison[, 1]),
    Method2 = mapply(combine_point_ci, est.comparison[, 2], ci.comparison[, 2]),
    Method3 = mapply(combine_point_ci, est.comparison[, 3], ci.comparison[, 3]),
    Method4 = mapply(combine_point_ci, est.comparison[, 4], ci.comparison[, 4]),
    Method5 = mapply(combine_point_ci, est.comparison[, 5], ci.comparison[, 5]),
    Method6 = mapply(combine_point_ci, est.comparison[, 6], ci.comparison[, 6]),
    Method7 = mapply(combine_point_ci, est.comparison[, 7], ci.comparison[, 7])
  )
  
  # Add row names (fungal names)
  rownames(combined.inf) <- c("Fusarium", "Scedosporium", "Lomentospora", 
                              "Aspergillus", "Mucorales")
  # Add column names (comparison methods)
  colnames(combined.inf) <- c("Pool", "Test&Pool", "Reference",
                               "BMA", "EXNEX", "BMA-2D", "EXNEX-2D")
  
  # Combine the results in a list
  case <- list(decision   = decision.comparison,
               evidence   = decision.evidence,
               estimate   = est.comparison,
               confidence = ci.comparison,
               inference  = combined.inf)
  return(case)
}
```


```{r}
## Generate case study data
set.seed(3)
## ----------------------------------------------------------------
s <- 4
sim_out <- sim.dat(n_soc = n_soc, n_trt = n_trt, 
                   p_soc = pmat0[s, ] + ni_mar, p_trt = pmat1[s, ])
trial_dat <- sim_out$raw_data
## ----------------------------------------------------------------
set.seed(NULL)
sim_out$summary_data
D42.Death.treatment <- sim_out$summary_data$y_trt/sim_out$summary_data$n_trt
D42.Death.control   <- sim_out$summary_data$y_soc/sim_out$summary_data$n_soc
D42.Death.differ    <- round(D42.Death.treatment - D42.Death.control, 2)
D42.Death.differ

Case.Study(trial_dat)
```


```{r}
## Generate case study data
set.seed(21)
## ----------------------------------------------------------------
s <- 6
sim_out <- sim.dat(n_soc = n_soc, n_trt = n_trt, 
                   p_soc = pmat0[s, ] + ni_mar, p_trt = pmat1[s, ])
trial_dat <- sim_out$raw_data
## ----------------------------------------------------------------
set.seed(NULL)
sim_out$summary_data
D42.Death.treatment <- sim_out$summary_data$y_trt/sim_out$summary_data$n_trt
D42.Death.control   <- sim_out$summary_data$y_soc/sim_out$summary_data$n_soc
D42.Death.differ    <- round(D42.Death.treatment - D42.Death.control, 2)
D42.Death.differ

Case.Study(trial_dat)
```



